---
title: "Meta_Analise"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## packages used
```{r}
citation()
citation("dplyr")
citation("tidyr")
citation("ggplot2")
citation("ggthemes")
```


## read summarized csv data create some variables on data frame
```{r}
#initialize packages
library(dplyr)
library(tidyr)


# Read csv data
df2 = read.csv("C:/Users/Elias/Documents/UNIOESTE/AnaliseDeDados/ProfLuiz/DadosWSCAD/evento_tipo_ano.csv",  header=TRUE, sep=";") 
#df2 = read.csv("C:/Users/Elias/Documents/UNIOESTE/AnaliseDeDados/ProfLuiz/Trabalho/meta_analise/SMPE-UFRGS-master/evento_tipo_ano.csv",  header=TRUE, sep=";") 

# Filtering only WSCAD conference
df2 = df2[df2$tipo!="EXT" & df2$evento=="WSCAD" ,] # filter only one category



# creates the relative frequency variable on data frame
df2 = df2 %>% 
     group_by(evento) %>% 
     mutate(freq_relat=n_art/total) %>%  
     mutate(freq_relat=round(freq_relat*100, 2))

# creates the citation ratio variable on data frame
df2 = df2 %>% 
     group_by(evento, tipo, ano) %>% 
     mutate(cit_ratio=n_ocur/n_art) %>%  
     mutate(cit_ratio=round(cit_ratio, 2))

# show data frame
df2


```

## declares a graph function 
```{r}

# parameters:
# vx - variable for x axxis
# vy - variable for y axxis
# lx - label for x axxis
# ly - label for y axxis
# gt - graphic tittle 

plot_gg <- function(vx, vy, lx, ly, gt)
{
  library(ggplot2)
  library(ggthemes)
  
  # initialize the graph with a shape for each value from TIPO
  graph = ggplot(data=df2, aes(x = vx, y = vy , shape=as.factor(tipo)))

  # set the color for each shape according to TIPO
  graph = graph + geom_point(aes(x = vx, y = vy , color=as.factor(tipo)), size=3)

  # set the x/y labels and graph types
  graph = graph + labs(x=lx, y=ly, title = gt)

  # set the graph side labels tittle 
  graph = graph  + scale_colour_brewer(palette="Dark2")

  # variable to pivot the graph
  graph = graph  + facet_wrap(~evento)
  
 # graph = graph  + geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

  # plot the graph
  graph
  
}


```

## Relative Frequency by tipo/ano for conference WSCAD
```{r}

plot_gg(df2$ano, df2$freq_relat, "Ano", "% Artigos", "")

```

## Citation Ratio by tipo/ano for conference WSCAD
```{r}

plot_gg(df2$ano, df2$cit_ratio,  "Ano", "Citações por Artigo", "")

```



## Summarizing Tables
### Table Estatistical Terms by year
```{r}
# Read raw csv data
df_raw = read.csv("C:/Users/Elias/Documents/UNIOESTE/AnaliseDeDados/ProfLuiz/DadosWSCAD/resultados.csv",  header=TRUE, sep=";") 
#df_raw = read.csv("C:/Users/Elias/Documents/UNIOESTE/AnaliseDeDados/ProfLuiz/Trabalho/meta_analise/SMPE-UFRGS-master/resultados.csv",  header=TRUE, sep=";") 


# Filtering only WSCAD conference and EST type
df_est = df_raw[df_raw$evento=="WSCAD" & df_raw$tipo=="EST",] # filter only one category

df_est = df_est   %>% 
  group_by( ano , termo) %>% 
  summarise(n= n())
df_est = spread(df_est, termo, n)
df_est
```

### Table Metric Terms by year
```{r}
# Filtering only WSCAD conference and MET type
df_met = df_raw[df_raw$evento=="WSCAD" & df_raw$tipo=="MET",] # filter only one category

df_met = df_met   %>% 
  group_by( ano , termo) %>% 
  summarise(n= n())
df_met = spread(df_met, termo, n)
df_met
```

### Table Estatistical Tests by year
```{r}
# Filtering only WSCAD conference and TST type
df_tst = df_raw[df_raw$evento=="WSCAD" & df_raw$tipo=="TST",] # filter only one category

df_tst = df_tst   %>% 
  group_by( ano , termo) %>% 
  summarise(n= n())
df_tst = spread(df_tst, termo, n)
df_tst

```

### Categorical distribuition by year
```{r}
# Filtering only WSCAD conference and just category of terms
df = df_raw[df_raw$evento=="WSCAD" ,] # filter only one category

df = df   %>% 
  group_by( ano , tipo) %>% 
  summarise(n= n())
df = spread(df, tipo, n)
df



```



#df_raw
#Visulizamos os distribuição dos termos estatiticos por ano

boxplot(df_raw$ano ~ df_raw$tipo)

#Executamos Análise de variância
#Observar valor de p maior que 0,05 (Pr(>F))
#Hipótese nula de que não há diferença significativa

an =  aov(ano ~ termo, data=df_raw)
summary(an)

#Anova de dois fatores
#Nenhum valor de P mostra diferença significativa

an =  aov(ano ~ termo * tipo, data=df_raw)
summary(an)



#Teste de Shapiro termos estatisticos
#Valor de p acima de 0,05, não há indício para a não confirmar a hipótese nula de dados normalmente #distribuidos

shapiro.test(df$EST)

#Media termos estatísticos
mean(df$EST)

#Gráfico QQ termos estatísticos

qqnorm(df$EST)
#linha
qqline(df$EST)

#Gráfico QQ metricas

qqnorm(df$MET)
#linha
qqline(df$MET)




#Histograma com linha de densidade
```{r}
#rodar com Ctrl+shift+enter
hist(df$EST, main="")
par(new=TRUE)
plot(density(df$EST),ylab = "", xlab = "", axes=F, lwd=2.5 ) 
```
```{r}
# Read raw csv data
df_raw = read.csv("C:/Users/Elias/Documents/UNIOESTE/AnaliseDeDados/ProfLuiz/DadosWSCAD/resultados2.csv",  header=TRUE, sep=";") 


# Filtering only WSCAD conference and just category of terms
df = df_raw[df_raw$evento=="WSCAD" ,] # filter only one category

df = df   %>% 
  group_by( ano , tipo) %>% 
  summarise(n= n())
df = spread(df, tipo, n)
df


```

## Correlation
```{r}
# exists corrlation between year and citation rate? it increase over the years?
cor.test(df2$ano, df2$cit_ratio)

l_m <- lm(formula = df2$ano ~ df2$cit_ratio)

l_m

summary(l_m)

```



